MLISA: Machine Learning-based \\ Intelligent Service Agents

### 2014-10-31 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

We utilize the same communities and web services with a simple rational decision making mechanism, in which communities would choose to join a community if it increases the utility by any amount. Figure \ref{utility_gain_mlisa_and_rational} shows the comparison in end result of utility gain values. In 18 out of 40 tries, rational agents have not been able to improve their utility at all, becuase the communities they have chosen have rejected their request since probably they would not increase the utility of the other communities if they have joined them. The results show a long term strategic decision mechanism is needed to satisfy all the services within communities with the cooperation. Figure \ref{utility_gain_mlisa_and_rational_ratio} shows the results of same experiment as ratio of utility gain.

@@

In order to evaluate the performance of the mechanism we have used \emph{receiver operating characteristic} or \emph{ROC curve}, which is a graphical plot illustrating true positive rate against the false positive rate at various threshold settings in classifier systems. In order to be able to classify our communities strategy selection as correct or not, for each community we ran the training process as if the community was already in the set instead of the closest one which its gets the strategy profile from. If actions are same and same utility levels are gained, we classify the decision as correct, otherwise its a wrong decision. The area under the \emph{ROC curve} called \emph{AUC} is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one\cite{xxx} and the higher number reflects better performance from the better solution.  Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of MLISA decision making mechanism. We compare our method with two other methods. The rational is based on assumption that communities as rational agents would join a community that increases their utility. And the then greedy method only looks up the available list of communities and joins the one that maximizes its utility without considering any long term strategy or the other communities acceptance scenario. Figure \ref{roc5} compares the results for all these methods. The two other methods have very high failure rate compared to our method. Table \ref{fail_rate} illustrates the number of communities which failed to find the optimal and best collaboration group.

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/roc.eps}
\caption{RoC Curve}
\label{roc5}
\end{figure}
Now we evaluate the system specific results from user and community perspective. By distributing tasks among the communities over these time frames we evaluate the revenue for each community. Figure \ref{stats1} shows the overall revenue gain of communities using our method. Figure \ref{stats2} shows the momentarily gain of revenue for each community on each time slot compared to previous time. These results show how the run with higher learning rate of $r=0.20$ start discovering better communities to join much earlier. The runs with slow rate seems to find some communities to join initially, then slow down until later where they start discovering new communities to join with.

>>>>

We utilize the same communities and web services with a simple rational decision making mechanism, in which communities would choose to join a community if it increases the utility by any amount. Figure \ref{utility_gain_mlisa_and_rational} shows the comparison of end result of utility gain values. In 18 out of 40 tries, rational agents have not been able to improve their utility at all, because the communities they have chosen have rejected their request since probably they would not increase the utility of the other communities if they have joined them. The results show a long term strategic decision mechanism is needed to satisfy all the services within communities with the cooperation. Figure \ref{utility_gain_mlisa_and_rational_ratio} shows the results of same experiment as ratio of utility gain.

@@

In order to evaluate the performance of the mechanism we have used \emph{receiver operating characteristic} or \emph{ROC curve}, which is a graphical plot illustrating true positive rate against the false positive rate at various threshold settings in classifier systems. In order to be able to classify our communities strategy selection as correct or not, for each community we evaluated the training process by replacing the community in set with the closest one which its gets the strategy profile from. If actions are same and same utility levels are gained, we classify the decision as correct, otherwise its a wrong decision. The area under the \emph{ROC curve} called \emph{AUC} is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one\cite{xxx} and the higher number reflects better performance from the better solution.  Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of MLISA decision making mechanism. We compare our method with two other methods. The rational is based on assumption that communities as rational agents would join a community that increases their utility. And the greedy method only looks up the available list of communities and joins the one that maximizes its utility without considering any long term strategy or the other communities acceptance scenario. Figure \ref{roc5} compares the results for all these methods. The two other methods have very high failure rate compared to our method. Table \ref{fail_rate} illustrates the number of communities which failed to find the optimal and best collaboration group. The results prove the need of a long term training model for successful decision making process.

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/roc.eps}
\caption{RoC Curve}
\label{roc5}
\end{figure}
Now we evaluate the system specific results from users and communities perspective. By distributing tasks among the communities over these time frames we evaluate the revenue for each community. Figure \ref{stats1} shows the overall revenue gain of communities using our method. Figure \ref{stats2} shows the momentarily gain of revenue for each community on each time slot compared to previous time. These results show how the run with higher learning rate of $r=0.20$ starts discovering better communities to join much earlier. The runs with slow rate seem to find some communities to join initially, then they slow down until later where they start discovering new communities to join with.
